negativeBinomial

### 2015-08-31 lengthModel/lengthModel.Rmd
bump

## Load the data
Note: ttestData.csv is missing two sites in the two-way anova data...

```{r}
library(ggplot2)
set.seed(123)
data_one_way <- read.csv("~/mysis/data/ttestData.csv", skip = 3, nrows = 40, header = TRUE)
# data_one_way$full ## count per m^2 for full net
# data_one_way$half ## count per m^2 for half net
count <- c(data_one_way$full.5,  ## count for full net
            4 * data_one_way$half.5) ## count for half net adjusted for radius
date <- rep(as.factor(data_one_way$month), 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(count=count, date=date, net=net)
X <- model.matrix(~ net * date)
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ .)
```

>>>>

## Load the data

```{r}
library(ggplot2)
set.seed(123)
data_length <- read.csv("~/mysis/data/lengthData.csv", skip = 4, header = TRUE)
net <- data_length$Size..m.
length <- data_length$Length..mm.
gender <- as.factor(substr(as.character(data_length$Gender), 0, 1))
# data_one_way$full ## count per m^2 for full net
# data_one_way$half ## count per m^2 for half net
count <- c(data_one_way$full.5,  ## count for full net
            4 * data_one_way$half.5) ## count for half net adjusted for radius
date <- rep(as.factor(data_one_way$month), 2)
net <- as.factor(c(rep("full", 40), rep("half", 40)))
data <- data.frame(count=count, date=date, net=net)
X <- model.matrix(~ net * date)
ggplot(data=data, aes(count)) + geom_histogram() + facet_grid(net ~ .)
```
